---
title: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(plotly)
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
dataset <- read.csv("CardiacPredictor/dataset.csv", sep=";", dec = ",")
```
<p style="font-family: Noto Sans, sans-serif; font-size:35pt; font-style:normal; color:#003A7D">
    <u>
    Data Interpretation
    </u>
</p>
<p><br></p>
# Injuries in Angioplasty
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
The number of injuries in the different blood vessels of the patients is important since both this and the injured vessels determine the complexity of the surgery and therefore the choice of procedure.
</p>
```{r echo=FALSE}
patientsWithAngioplasty <- subset(dataset,dataset$PROCEDIMIENTO == "ANGIOPLASTIA")

zeroInjuries <- 12
oneInjury <- 78
twoInjuries <- 79
threeInjuries <- 25
fourInjuries <- 6
library(plotly)
library(ggplot2)
x <- c('0', '1', '2', '3', '4')
y <- c(zeroInjuries, oneInjury, twoInjuries, threeInjuries, fourInjuries)
data <- data.frame(x, y)

fig <- plot_ly(data, x = ~x, y = ~y, type = 'bar',
             text = y, textposition = 'auto',
             marker = list(color = '#8ACBDE',
                           line = list(color = '#8ACBDE', width = 1.5)))
fig <- fig %>% layout(title = "",
         xaxis = list(title = "Number of Injuries"),
         yaxis = list(title = "Number of Patients"))

fig
```
# Extracorporeal circulation
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
Extracorporeal circulation refers to the circulation of blood outside of the body through a machine that temporarily assumes an organ's functions (eg. heart and lungs). The following bar graph shows the immediate complications on patients who underwent open heart surgery and extracorporeal circulation compared to those who did not have extracorporeal circulation. 
</p>
```{r echo=FALSE}
CEC<-subset(dataset,dataset$CIRCULACION.EXTRACORPOREA!="NO")
CECNO<-subset(dataset,dataset$CIRCULACION.EXTRACORPOREA=="NO")
immediateComplicationsCEC<-sum(CEC$COMPLICACIONES.INMEDIATAS == 1)
noimmediateComplicationsCEC <-sum(CEC$COMPLICACIONES.INMEDIATAS == 0)
immediateComplicationsCECNO <-sum(CECNO$COMPLICACIONES.INMEDIATAS == 1)
noimmediateComplicationsCECNO <-sum(CECNO$COMPLICACIONES.INMEDIATAS == 0)
library(plotly)

x <- c('CEC', 'Without CEC')
y <- c(immediateComplicationsCEC,immediateComplicationsCECNO)
y2 <- c(noimmediateComplicationsCEC,noimmediateComplicationsCECNO)
data <- data.frame(x, y, y2)

immediateComplicationsAndCEC <- data %>% plot_ly()
immediateComplicationsAndCEC <- immediateComplicationsAndCEC %>% add_trace(x = ~x, y = ~y, type = 'bar',
                         name = 'With Complications',
                         text = y, textposition = 'auto',
                         marker = list(color = '#F86F6F',
                                       line = list(color = '#F86F6F', width = 1.5)))
immediateComplicationsAndCEC <- immediateComplicationsAndCEC %>% add_trace(x = ~x, y = ~y2, type = 'bar',
                         name = 'Without Complications',
                         text = y2, textposition = 'auto',
                         marker = list(color = '#003A7D',
                                       line = list(color = '#003A7D', width = 1.5)))
immediateComplicationsAndCEC <- immediateComplicationsAndCEC %>% layout(title = "",
                      barmode = 'group',
                      xaxis = list(title = ""),
                      yaxis = list(title = "Number of Patients"))

immediateComplicationsAndCEC
```
# Hyperlactic patients with Post-Op Complications
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
Hyperlactatemia is the elevated quantity of lactate in blood. While a normal blood lactate level is between 0-2mmol/L, a patient with hyperlactatemia has a level above 3-5mmol/L. When this alteration arises in the operating room or very early in the ICU (early-onset hyperlactatemia), it is strongly associated with adverse outcomes and complications, while late-onset (6-12h in the ICU) is a benign alteration that spontaneously resolves itself within 24 hours. Between the 53 early-onset hyperlactic patients in surgery, 28 of them had complications.
</p>
```{r echo=FALSE}
library(ggplot2)
library(plotly)
surgerySubset <- subset(dataset,dataset$PROCEDIMIENTO=="CIRUGIA")
HyperLactHistogram2 <- plot_ly(type='histogram',
                              x=surgerySubset$LACTICO.POP,
                              bingroup=1, name = "Total Patients", 
                              marker = 
                                list(color= "#2093C3",
                                     line=list(color="darkgray",width=0.0))
                              ,nbinsx=100)

surgeryComplications <- subset(surgerySubset, surgerySubset$COMPLICACIONES.INMEDIATAS >=1 
                               | surgerySubset$COMPLICACIONES.TARDIAS >= 1)

HyperLactHistogram2 <- HyperLactHistogram2 %>% add_histogram(
  type = 'histogram',
  x = surgeryComplications$LACTICO.POP,
  bingroup=1, name = "Patients with Complications", 
  marker = 
    list(color= "#F86F6F",
         line=list(color="darkgray",width=0.0))
  ,nbinsx=100)
HyperLactHistogram2 <- HyperLactHistogram2 %>% layout(barmode = "overlay", 
                                  xaxis = list(title = "Post-Op Lactate in Blood (mmol/L)")
                                  ,yaxis = list(title = "Number of Patients"))
HyperLactHistogram2

```
# Severe LVEF values and Post-Op complications
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
    Many researches have shown that LVEF values have relation with Post-Op surgery complications (hence, the need to study it in our project). Between the 11 patients in surgery with severe LVEF values, 7 of them had complications.
</p>
```{r echo=FALSE}
library(plotly)
severeFey <- subset(dataset,dataset$FEY<=40)
severeFeySurgery <- subset(severeFey,severeFey$PROCEDIMIENTO=="CIRUGIA")
severeFeySurgeryComplications <- round(sum(severeFeySurgery$COMPLICACIONES.INMEDIATAS==1)/length(severeFeySurgery$COMPLICACIONES.INMEDIATAS)*100)
severeFeySurgeryNOComplications <- round(sum(severeFeySurgery$COMPLICACIONES.INMEDIATAS==0)/length(severeFeySurgery$COMPLICACIONES.INMEDIATAS)*100)
FeySevPieval<- c(severeFeySurgeryNOComplications,severeFeySurgeryComplications)
FeySevPielabels<- c(paste("Without: ",severeFeySurgeryNOComplications,"%"),paste("With: ",severeFeySurgeryComplications,"%"))
feySevPie <- plot_ly(type = 'pie', 
                     labels = FeySevPielabels, 
                     values = FeySevPieval,
                     textinfo='label',
                     insidetextorientation='radial',
                     marker = list(colors = c("#003A7D","#F86F6F")),
                     title = ""
                     )
feySevPie
```
# Complications in male patients older than 60 years
***
<p style="font-family:Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
    The differences in complications between patients who had angioplasty and open heart surgery in this dataset are shown in the next bar graph. 
</p>
```{r echo=FALSE}
menOlderThan60<- subset(dataset, dataset$EDAD >= 60 & dataset$SEXO == "MASC")
menOlderThan60WithAngioplasty<- subset(menOlderThan60, menOlderThan60$PROCEDIMIENTO == "ANGIOPLASTIA")
menOlderThan60WithSurgery <- subset(menOlderThan60, menOlderThan60$PROCEDIMIENTO == "CIRUGIA")

library(plotly)
library(ggplot2)
x <- c("Angioplasty", "Surgery - Immediate", "Surgery- Late")
y1 <- c(sum(menOlderThan60WithAngioplasty$COMPLICACIONES.ANGIOPLASTIA== 0), sum(menOlderThan60WithSurgery$COMPLICACIONES.INMEDIATAS == 0), sum(menOlderThan60WithSurgery$COMPLICACIONES.TARDIAS == 0) )
y2<- c(sum(menOlderThan60WithAngioplasty$COMPLICACIONES.ANGIOPLASTIA == 1), sum(menOlderThan60WithSurgery$COMPLICACIONES.INMEDIATAS == 1), sum(menOlderThan60WithSurgery$COMPLICACIONES.TARDIAS == 1))
data <- data.frame(x, y1, y2)

complicationsInMenOlderThan60 <- plot_ly(data, x = ~x, y = ~y1, type = 'bar', name = 'Without Complications', marker = list(color = '#003A7D'))
complicationsInMenOlderThan60 <- complicationsInMenOlderThan60 %>% add_trace(y = ~y2, name = 'With Complications', marker = list(color = '#F86F6F'))
complicationsInMenOlderThan60 <- complicationsInMenOlderThan60 %>% layout(xaxis = list(title = "", tickangle = 0),
                      yaxis = list(title = "Number of Patients"),
                      margin = list(b = 100),
                      barmode = 'group')
complicationsInMenOlderThan60
```
# Female patients older than 60 years whose reason for admission was valve programming and had an open heart surgery
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
</p>
```{r echo=FALSE}
surgeryInWomenOlderThan60<- subset(dataset, dataset$EDAD >= 60 & dataset$SEXO == "FEME" & dataset$PROCEDIMIENTO== "CIRUGIA")
progValv <- round(sum(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO == "PROG VALV")/length(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO)*100, 2)
progCoronary <- round(sum(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO == "PROG CORONARIO")/length(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO)*100,2)
others <- round(sum(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO == "ANEURISMA AO")/length(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO)*100,2)

library(ggplot2)
library(plotly)
dataEntryToHospital <- c(progValv, progCoronary, others)

entryWomenOlderThan60ForSurgery <- plot_ly(type = 'pie', 
                     labels = c("Valve Prog", "Coronary Prog", "Others"), 
                     values = dataEntryToHospital,
                     textinfo='label',
                     insidetextorientation='radial',
                     marker = list(colors = c("#8ACBDE","#003A7D", "#C5C6D0")),
                     title = ""
                     )
entryWomenOlderThan60ForSurgery

```
<p style="font-family: Noto Sans, sans-serif; font-size:20pt; font-style:normal; color:#000000">
    Procedures in male patients with morbid obesity
</p>
***
<p style="font-family: Georgia, serif; font-size:13pt; font-style:normal; color:#000000">
</p>
```{r echo=FALSE}
library(plotly)
morbidObesity <- subset(dataset,dataset$OBESIDAD.MORBIDA == 1)
labels = c('ANGIOPLASTY','SURGERY','ENDOVALVE')
values = c(sum(morbidObesity$PROCEDIMIENTO == "ANGIOPLASTIA"), sum(morbidObesity$PROCEDIMIENTO == "CIRUGIA"), sum(morbidObesity$PROCEDIMIENTO == "ENDOVALVULA"))

morbidObesityAndProcedures <- plot_ly(type='pie', labels=labels, values=values, 
               textinfo='label+percent',
               marker = list(colors = c("#8ACBDE","#003A7D", "#C5C6D0")),
               insidetextorientation='radial')
morbidObesityAndProcedures
```
# Immediate and late complications in open heart surgery
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
</p>
```{r echo=FALSE}
library(plotly)

CRM_PURE<-subset(dataset,dataset$TIPO.DE.CIRUGIA=="CRM PURA")
immediateComplicationsCRM_PURE<-round(sum(CRM_PURE$COMPLICACIONES.INMEDIATAS == 1)/length(CRM_PURE)*100, digits=2)
lateComplicationsCRM_PURE<-round(sum(CRM_PURE$COMPLICACIONES.TARDIAS == 1)/length(CRM_PURE)*100, digits=2)

RVAO<-subset(dataset,dataset$TIPO.DE.CIRUGIA=="RVAO")
immediateComplicationsRVAO<-round(sum(RVAO$COMPLICACIONES.INMEDIATAS == 1)/length(RVAO)*100, digits=2)
lateComplicationsRVAO<-round(sum(RVAO$COMPLICACIONES.TARDIAS == 1)/length(RVAO)*100, digits=2)

mitralPlastic<-subset(dataset,dataset$TIPO.DE.CIRUGIA=="PLASTICA MITRAL")
immediateComplicationsMitralPlastic<-round(sum(mitralPlastic$COMPLICACIONES.INMEDIATAS == 1)/length(mitralPlastic)*100, digits=2)
lateComplicationsMitralPlastic<-round(sum(mitralPlastic$COMPLICACIONES.TARDIAS == 1)/length(mitralPlastic)*100, digits=2)

RVAo_Aorta<-subset(dataset,dataset$TIPO.DE.CIRUGIA=="RVAo + Aorta")
immediateComplicationsRVAo_Aorta<-round(sum(RVAo_Aorta$COMPLICACIONES.INMEDIATAS == 1)/length(RVAo_Aorta)*100, digits=2)
lateComplicationsRVAo_Aorta<-round(sum(RVAo_Aorta$COMPLICACIONES.TARDIAS == 1)/length(RVAo_Aorta)*100, digits=2)

x <- c('CRM PURA', 'RVAO', 'PLÃSTICA MITRAL', 'RVAo + Aorta')#nombres de c.
y <- c(immediateComplicationsCRM_PURE, immediateComplicationsRVAO,immediateComplicationsMitralPlastic, immediateComplicationsRVAo_Aorta)
y2 <- c(lateComplicationsCRM_PURE,lateComplicationsRVAO,lateComplicationsMitralPlastic, lateComplicationsRVAo_Aorta)
data <- data.frame(x, y)

complicationsInSurgery<- data %>% plot_ly()
complicationsInSurgery <- complicationsInSurgery %>% add_trace(x = ~x, y = ~y, type = 'bar',
                         name = 'Immediate Complications',#inmediatas
                         text = y, textposition = 'auto',
                         marker = list(color = '#8ACBDE',
                                       line = list(color = '#8ACBDE', width = 1.5)))
complicationsInSurgery <- complicationsInSurgery %>% add_trace(x = ~x, y = ~y2, type = 'bar',
                         name = 'Late Complications',#tardias
                         text = y2, textposition = 'auto',
                         marker = list(color = '#C5C6D0',
                                       line = list(color = '#C5C6D0', width = 1.5)))
complicationsInSurgery <- complicationsInSurgery %>% layout(title = "",
                      barmode = 'group',
                      xaxis = list(title = ""),
                      yaxis = list(title = "% of Complications"))

complicationsInSurgery
```
# Previous angioplasty patients who had a second angioplasty
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
    We found that many patients who had undergone an angioplasty, had had another one performed on them. The cause for this phenomenon may be that the arteries are blocked or obstructed again (it could be the same or other arteries) which is not a rare risk of a first angioplasty.
</p>
```{r echo=FALSE}
library(tidyr)
previousInterventionAngioplasty <- subset(dataset, dataset$INTERVENCION.PREVIA=="ANGIOPLASTIA")
moreThan1Angioplasty <- sum(previousInterventionAngioplasty$PROCEDIMIENTO == "ANGIOPLASTIA")
only1Angioplasty <- sum(previousInterventionAngioplasty$PROCEDIMIENTO != "ANGIOPLASTIA")
dataset2 <- dataset
dataset2$INTERVENCION.PREVIA <- replace_na("T")
firstAngio <- sum(dataset2$INTERVENCION.PREVIA!="ANGIOPLASTIA" & dataset2$PROCEDIMIENTO=="ANGIOPLASTIA")
noAngio <- sum(dataset2$INTERVENCION.PREVIA!="ANGIOPLASTIA" & dataset2$PROCEDIMIENTO!="ANGIOPLASTIA")
library(plotly)
x <- c('Prev: Angioplasty', 'Prev: Others')
y <- c(moreThan1Angioplasty,firstAngio)
y2 <- c(only1Angioplasty,noAngio)
data <- data.frame(x, y, y2)

angioplasties<- data %>% plot_ly()
angioplasties <- angioplasties %>% add_trace(x = ~x, y = ~y, type = 'bar',
                         name = 'Angioplasty',
                         text = y, textposition = 'auto',
                         marker = list(color = '#8ACBDE',
                                       line = list(color = '#8ACBDE', width = 1.5)))
angioplasties <- angioplasties %>% add_trace(x = ~x, y = ~y2, type = 'bar',
                         name = 'Different Procedure',
                         text = y2, textposition = 'auto',
                         marker = list(color = '#C5C6D0',
                                       line = list(color = '#C5C6D0', width = 1.5)))
angioplasties <- angioplasties %>% layout(title = "",
                      barmode = 'group',
                      xaxis = list(title = ""),
                      yaxis = list(title = "Number of Patients"))

angioplasties
```

# Diabetic patients and coronary programmed 
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">
</p>
```{r echo=FALSE}
diabetics <- sum(dataset$DIABETES == 1)
coronary <- sum(dataset$MOTIVO.DE.INGRESO == "PROG CORONARIO")
subsetCoronary <- subset(dataset,dataset$MOTIVO.DE.INGRESO == "PROG CORONARIO")
crossedArea <- sum(subsetCoronary$DIABETES == 1)
library("VennDiagram") 
grid.newpage()
g = draw.pairwise.venn(area1 = diabetics,
                   area2 = coronary,
                   cross.area = crossedArea,
                   category = c("Programmed Coronary", "Diabetic Patients"),
                   fill = c("#8ACBDE","#F86F6F"),
                   lty = "blank",
                   inverted = TRUE)
```
# Complications in open heart surgery patients who entered for Programmed Coronary
***
<p style="font-family: Noto Sans, sans-serif; font-size:13pt; font-style:normal; color:#000000">

</p>
```{r echo=FALSE}
library(plotly)
ProgYCirujia <- subset(dataset,dataset$MOTIVO.DE.INGRESO=="PROG CORONARIO" & dataset$PROCEDIMIENTO=="CIRUGIA") 

immediateComplicationsProgYCirujia<-round(sum(ProgYCirujia$COMPLICACIONES.INMEDIATAS == 1))
noImmediateComplicationsProgYCirujia<-round(sum(ProgYCirujia$COMPLICACIONES.INMEDIATAS == 0))


lateComplicationsProgYCirujia<-round(sum(ProgYCirujia$COMPLICACIONES.TARDIAS == 1))
noLateComplicationsProgYCirujia<-round(sum(ProgYCirujia$COMPLICACIONES.TARDIAS == 0))

x <- c('Immediate Complications', 'Late Complications')#nombres de c.
y <- c(immediateComplicationsProgYCirujia, lateComplicationsProgYCirujia)
y2 <- c(noImmediateComplicationsProgYCirujia, noLateComplicationsProgYCirujia)
data <- data.frame(x, y)

complicationsInSurgery<- data %>% plot_ly()
complicationsInSurgery <- complicationsInSurgery %>% add_trace(x = ~x, y = ~y, type = 'bar',
                         name = 'Yes',#inmediatas
                         text = y, textposition = 'auto',
                         marker = list(color = '#003A7D',
                                       line = list(color = '#003A7D', width = 1.5)))
complicationsInSurgery <- complicationsInSurgery %>% add_trace(x = ~x, y = ~y2, type = 'bar',
                         name = 'No',#tardias
                         text = y2, textposition = 'auto',
                         marker = list(color = '#8ACBDE', 
                                       line = list(color = '#8ACBDE', width = 1.5)))
complicationsInSurgery <- complicationsInSurgery %>% layout(title = "",
                      barmode = 'group',
                      xaxis = list(title = ""),
                      yaxis = list(title = "Number of pacients"))

complicationsInSurgery
```

