---
title: "INTERPRETATION"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(plotly)
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
dataset <- read.csv("LabJournalWebsite/dataset.csv", sep=";")
```


#Number of injuries of people who went to angioplasty 
***
The number of injuries in the different blood vessels is important since both this and the injured vessels determine the complexity of the surgery and therefore the choice of procedure

```{r echo=FALSE}
patientsWithAngioplasty <- subset(dataset,dataset$PROCEDIMIENTO == "ANGIOPLASTIA")
#numero0 <- sum(personasConAngioplastia$NUMERO.DE.LESIONES==0)
#numero1 <- sum(personasConAngioplastia$NUMERO.DE.LESIONES==1)
#numero2 <- sum(personasConAngioplastia$NUMERO.DE.LESIONES==2)
#numero3 <- sum(personasConAngioplastia$NUMERO.DE.LESIONES==3)
#numero4 <- sum(personasConAngioplastia$NUMERO.DE.LESIONES==4)
zeroInjuries <- 12
oneInjury <- 78
twoInjuries <- 79
threeInjuries <- 25
fourInjuries <- 6
library(plotly)
library(ggplot2)
x <- c('0', '1', '2', '3', '4')
y <- c(zeroInjuries, oneInjury, twoInjuries, threeInjuries, fourInjuries)
data <- data.frame(x, y)

fig <- plot_ly(data, x = ~x, y = ~y, type = 'bar',
             text = y, textposition = 'auto',
             marker = list(color = '#546FBF',
                           line = list(color = '#546FBF', width = 1.5)))
fig <- fig %>% layout(title = "",
         xaxis = list(title = "Number of Injuries"),
         yaxis = list(title = "Number of Patients"))

fig
```



# Extracorporeal circulation
***

Risk of immediate complications on patients who underwent surgery and doctors need to use extracorporeal circulation compared to those who did not have extracorporeal circulation. Extracorporeal circulation refers to the circulation of blood outside of the body through a machine that temporarily assumes an organ's functions (eg. heart and lungs).
```{r echo=FALSE}
CEC<-subset(dataset,dataset$CIRCULACION.EXTRACORPOREA!="NO")
CECNO<-subset(dataset,dataset$CIRCULACION.EXTRACORPOREA=="NO")
immediateComplicationsCEC<-sum(CEC$COMPLICACIONES.INMEDIATAS == 1)
noimmediateComplicationsCEC <-sum(CEC$COMPLICACIONES.INMEDIATAS == 0)
immediateComplicationsCECNO <-sum(CECNO$COMPLICACIONES.INMEDIATAS == 1)
noimmediateComplicationsCECNO <-sum(CECNO$COMPLICACIONES.INMEDIATAS == 0)
library(plotly)

x <- c('CEC', 'Without CEC')
y <- c(immediateComplicationsCEC,immediateComplicationsCECNO)
y2 <- c(noimmediateComplicationsCEC,noimmediateComplicationsCECNO)
data <- data.frame(x, y, y2)

immediateComplicationsAndCEC <- data %>% plot_ly()
immediateComplicationsAndCEC <- immediateComplicationsAndCEC %>% add_trace(x = ~x, y = ~y, type = 'bar',
                         name = 'With Complications',
                         text = y, textposition = 'auto',
                         marker = list(color = '#F24B4B',
                                       line = list(color = '#F24B4B', width = 1.5)))
immediateComplicationsAndCEC <- immediateComplicationsAndCEC %>% add_trace(x = ~x, y = ~y2, type = 'bar',
                         name = 'Without Complications',
                         text = y2, textposition = 'auto',
                         marker = list(color = '#546FBF',
                                       line = list(color = '#546FBF', width = 1.5)))
immediateComplicationsAndCEC <- immediateComplicationsAndCEC %>% layout(title = "Immediate Complications in Pacients with and without CEC",
                      barmode = 'group',
                      xaxis = list(title = ""),
                      yaxis = list(title = "Number of Patients"))

immediateComplicationsAndCEC
```



# Hyperlactic patients with Post-Op Complications
***

Hyperlactatemia is the elevated quantity of lactate in blood. While a normal blood lactate level is between 0-2mmol/L, a patient with hyperlactatemia has a level above 3-5mmol/L. When this alteration arises in the operating room or very early in the ICU (early-onset hyperlactatemia), it is strongly associated with adverse outcomes and complications, while late-onset (6-12h in the ICU) is a benign alteration that spontaneously resolves itself within 24 hours. 
Between the 53 early-onset hyperlactic patients in surgery, 28 of them had complications.


```{r echo=FALSE}
library(plotly)
hyperLact <- subset(dataset,dataset$LACTICO.POP>=3)
complicsHyperLact <- subset(hyperLact,hyperLact$COMPLICACIONES.INMEDIATAS==1 | hyperLact$COMPLICACIONES.TARDIAS==1)
hyperLactCir <- subset(hyperLact,hyperLact$PROCEDIMIENTO=="CIRUGIA")
hyperlactCirCompli <- round(sum(hyperLactCir$COMPLICACIONES.INMEDIATAS==1 | hyperLactCir$COMPLICACIONES.TARDIAS==1)/length(hyperLactCir$COMPLICACIONES.INMEDIATAS)*100)
hyperLactCirNorm <- round(sum(hyperLactCir$COMPLICACIONES.INMEDIATAS==0 & hyperLactCir$COMPLICACIONES.TARDIAS==0)/length(hyperLactCir$COMPLICACIONES.INMEDIATAS)*100)
hyperLactPieval<- c(hyperLactCirNorm,hyperlactCirCompli)
hyperLactpielabels<- c(paste("Without: ",hyperLactCirNorm,"%"),paste("With: ",hyperlactCirCompli,"%"))

hyperLactPie <- plot_ly(type = 'pie',
                        labels = hyperLactpielabels,
                        values = hyperLactPieval,
                        textinfo = 'label',
                        insidetextorientation ='radial',
                        marker = list(colors = c("#546FBF","#F24B4B")),
                        title = "Complications in Hyperlactic patients"
                        )
      
hyperLactPie
```

# Patients with severe LVEF values with Post-Op complications
***
Many studies have shown that LVEF values have relation with Post-Op surgery complications. Between the 11 patients in surgery with severe LVEF values, 7 of them had complications.

```{r echo=FALSE}
library(plotly)
severeFey <- subset(dataset,dataset$FEY<=40)
severeFeySurgery <- subset(severeFey,severeFey$PROCEDIMIENTO=="CIRUGIA")
severeFeySurgeryComplications <- round(sum(severeFeySurgery$COMPLICACIONES.INMEDIATAS==1)/length(severeFeySurgery$COMPLICACIONES.INMEDIATAS)*100)
severeFeySurgeryNOComplications <- round(sum(severeFeySurgery$COMPLICACIONES.INMEDIATAS==0)/length(severeFeySurgery$COMPLICACIONES.INMEDIATAS)*100)
FeySevPieval<- c(severeFeySurgeryNOComplications,severeFeySurgeryComplications)
FeySevPielabels<- c(paste("Without: ",severeFeySurgeryNOComplications,"%"),paste("With: ",severeFeySurgeryComplications,"%"))
feySevPie <- plot_ly(type = 'pie', 
                     labels = FeySevPielabels, 
                     values = FeySevPieval,
                     textinfo='label',
                     insidetextorientation='radial',
                     marker = list(colors = c("#546FBF","#F24B4B")),
                     title = ""
                     )
feySevPie
```

# Difference between angioplasty complications and surgical complications in men older than 60 years (late and immediate)

***

```{r echo=FALSE}
personasMayoresa60Hombres<- subset(dataset, dataset$EDAD >= 60 & dataset$SEXO == "MASC")
personasMayores60ConAngioplastiaHombres<- subset(personasMayoresa60Hombres, personasMayoresa60Hombres$PROCEDIMIENTO == "ANGIOPLASTIA")
complicacionesAngioplastiaMayores60Hombres <- table(personasMayores60ConAngioplastiaHombres$COMPLICACIONES.ANGIOPLASTIA)
personasMayores60ConCirugiaHombres <- subset(personasMayoresa60Hombres, personasMayoresa60Hombres$PROCEDIMIENTO == "CIRUGIA")
complicacionesCirugiaMayores60INMEDIATASHombres <- table(personasMayores60ConCirugiaHombres$COMPLICACIONES.INMEDIATAS)
complicacionesCirugiaMayores60TARDIASHombres <- table(personasMayores60ConCirugiaHombres$COMPLICACIONES.TARDIAS)


complicacionesAngioplastia1 <- sum(personasMayores60ConAngioplastiaHombres$COMPLICACIONES.ANGIOPLASTIA == 1)
complicacionesAngioplastia0 <- sum(personasMayores60ConAngioplastiaHombres$COMPLICACIONES.ANGIOPLASTIA== 0)
complicacionesCirugiaInmediata1 <- sum(personasMayores60ConCirugiaHombres$COMPLICACIONES.INMEDIATAS == 1) 
complicacionesCirugiaInmediata0 <- sum(personasMayores60ConCirugiaHombres$COMPLICACIONES.INMEDIATAS == 0)
complicacionesCirugiaTardia1 <- sum(personasMayores60ConCirugiaHombres$COMPLICACIONES.TARDIAS == 1)
complicacionesCirugiaTardia0 <- sum(personasMayores60ConCirugiaHombres$COMPLICACIONES.TARDIAS == 0)

library(plotly)
library(ggplot2)
x <- c("Angioplasty Complications", "Immediate Surgery Complications", "Late Surgery Complications")
y1 <- c(complicacionesAngioplastia0, complicacionesCirugiaInmediata0, complicacionesCirugiaTardia0)
y2<- c(complicacionesAngioplastia1, complicacionesCirugiaInmediata1, complicacionesCirugiaInmediata1)
data2 <- data.frame(x, y1, y2)

data2$x <- factor(data2$x, levels = data2[["x"]])
fig6 <- plot_ly(data2, x = ~x, y = ~y1, type = 'bar', name = 'Without Complications', marker = list(color = '#1f63b4'))
fig6 <- fig6 %>% add_trace(y = ~y2, name = 'With Complications', marker = list(color = '#d60409'))
fig6 <- fig6 %>% layout(xaxis = list(title = "", tickangle = 0),
                      yaxis = list(title = ""),
                      margin = list(b = 100),
                      barmode = 'group')
fig6
```

# Women older than 60 years whose reason for admission was valve programming and went to surgery
***


```{r echo=FALSE}
surgeryInWomenOlderThan60<- subset(dataset, dataset$EDAD >= 60 & dataset$SEXO == "FEME" & dataset$PROCEDIMIENTO== "CIRUGIA")
progValv <- round(sum(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO == "PROG VALV")/length(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO)*100, 2)
progCoronary <- round(sum(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO == "PROG CORONARIO")/length(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO)*100,2)
others <- round(sum(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO == "ANEURISMA AO")/length(surgeryInWomenOlderThan60$MOTIVO.DE.INGRESO)*100,2)

library(ggplot2)
library(plotly)
dataEntryToHospital <- c(progValv, progCoronary, others)

entryWomenOlderThan60ForSurgery <- plot_ly(type = 'pie', 
                     labels = c("Valve Prog", "Coronary Prog", "Others"), 
                     values = dataEntryToHospital,
                     textinfo='label',
                     insidetextorientation='radial',
                     marker = list(colors = c("#546FBF","#F24B4B", "#D0D9F2")),
                     title = "Complications in LFEV patients"
                     )
entryWomenOlderThan60ForSurgery

```

# Morbidly obese male patients and their procedures

***

```{r echo=FALSE}
library(plotly)
morbidObesity <- subset(dataset,dataset$OBESIDAD.MORBIDA == 1)
labels = c('ANGIOPLASTY','SURGERY','ENDOVALVE')
values = c(sum(morbidObesity$PROCEDIMIENTO == "ANGIOPLASTIA"), sum(morbidObesity$PROCEDIMIENTO == "CIRUGIA"), sum(morbidObesity$PROCEDIMIENTO == "ENDOVALVULA"))

morbidObesityAndProcedures <- plot_ly(type='pie', labels=labels, values=values, 
               textinfo='label+percent',
               marker = list(colors = c("#546FBF","#F24B4B", "#D0D9F2")),
               insidetextorientation='radial')
morbidObesityAndProcedures
```

# Analysis of the immediate and late complications of each type of open heart surgery

***
```{r echo=FALSE}
library(plotly)

CRM_PURE<-subset(dataset,dataset$TIPO.DE.CIRUGIA=="CRM PURA")
immediateComplicationsCRM_PURE<-round(sum(CRM_PURE$COMPLICACIONES.INMEDIATAS == 1)/length(CRM_PURE)*100, digits=2)
lateComplicationsCRM_PURE<-round(sum(CRM_PURE$COMPLICACIONES.TARDIAS == 1)/length(CRM_PURE)*100, digits=2)

RVAO<-subset(dataset,dataset$TIPO.DE.CIRUGIA=="RVAO")
immediateComplicationsRVAO<-round(sum(RVAO$COMPLICACIONES.INMEDIATAS == 1)/length(RVAO)*100, digits=2)
lateComplicationsRVAO<-round(sum(RVAO$COMPLICACIONES.TARDIAS == 1)/length(RVAO)*100, digits=2)

mitralPlastic<-subset(dataset,dataset$TIPO.DE.CIRUGIA=="PLASTICA MITRAL")
immediateComplicationsMitralPlastic<-round(sum(mitralPlastic$COMPLICACIONES.INMEDIATAS == 1)/length(mitralPlastic)*100, digits=2)
lateComplicationsMitralPlastic<-round(sum(mitralPlastic$COMPLICACIONES.TARDIAS == 1)/length(mitralPlastic)*100, digits=2)

RVAo_Aorta<-subset(dataset,dataset$TIPO.DE.CIRUGIA=="RVAo + Aorta")
immediateComplicationsRVAo_Aorta<-round(sum(RVAo_Aorta$COMPLICACIONES.INMEDIATAS == 1)/length(RVAo_Aorta)*100, digits=2)
lateComplicationsRVAo_Aorta<-round(sum(RVAo_Aorta$COMPLICACIONES.TARDIAS == 1)/length(RVAo_Aorta)*100, digits=2)

x <- c('CRM PURA', 'RVAO', 'PLÃSTICA MITRAL', 'RVAo + Aorta')#nombres de c.
y <- c(immediateComplicationsCRM_PURE, immediateComplicationsRVAO,immediateComplicationsMitralPlastic, immediateComplicationsRVAo_Aorta)
y2 <- c(lateComplicationsCRM_PURE,lateComplicationsRVAO,lateComplicationsMitralPlastic, lateComplicationsRVAo_Aorta)
data <- data.frame(x, y)

complicationsInSurgery<- data %>% plot_ly()
complicationsInSurgery <- complicationsInSurgery %>% add_trace(x = ~x, y = ~y, type = 'bar',
                         name = 'Immediate Complications',#inmediatas
                         text = y, textposition = 'auto',
                         marker = list(color = '#F24B4B',
                                       line = list(color = '#F24B4B', width = 1.5)))
complicationsInSurgery <- complicationsInSurgery %>% add_trace(x = ~x, y = ~y2, type = 'bar',
                         name = 'Late Complications',#tardias
                         text = y2, textposition = 'auto',
                         marker = list(color = '#546FBF',
                                       line = list(color = '#546FBF', width = 1.5)))
complicationsInSurgery <- complicationsInSurgery %>% layout(title = "Immediate and Late Complications in Pacients with different types of surgery",
                      barmode = 'group',
                      xaxis = list(title = ""),
                      yaxis = list(title = "% of Complications"))

complicationsInSurgery
```

# Previous angioplasty patients who had a re-angioplasty
***
We found that many patients who had undergone an angioplasty, had had another one. The cause for this phenomenon may be that the arteries are blocked or obstructed again (it could be the same or other arteries) which is not a rare risk of a first angioplasty.


```{r echo=FALSE}
library(tidyr)
previousInterventionAngioplasty <- subset(dataset, dataset$INTERVENCION.PREVIA=="ANGIOPLASTIA")
moreThan1Angioplasty <- sum(previousInterventionAngioplasty$PROCEDIMIENTO == "ANGIOPLASTIA")
only1Angioplasty <- sum(previousInterventionAngioplasty$PROCEDIMIENTO != "ANGIOPLASTIA")
dataset2 <- dataset
dataset2$INTERVENCION.PREVIA <- replace_na("T")
firstAngio <- sum(dataset2$INTERVENCION.PREVIA!="ANGIOPLASTIA" & dataset2$PROCEDIMIENTO=="ANGIOPLASTIA")
noAngio <- sum(dataset2$INTERVENCION.PREVIA!="ANGIOPLASTIA" & dataset2$PROCEDIMIENTO!="ANGIOPLASTIA")
library(plotly)
x <- c('Prev: Angioplasty', 'Prev: Others')
y <- c(moreThan1Angioplasty,firstAngio)
y2 <- c(only1Angioplasty,noAngio)
data <- data.frame(x, y, y2)

angioplasties<- data %>% plot_ly()
angioplasties <- angioplasties %>% add_trace(x = ~x, y = ~y, type = 'bar',
                         name = 'Angioplasty',
                         text = y, textposition = 'auto',
                         marker = list(color = '#F24B4B',
                                       line = list(color = '#F24B4B', width = 1.5)))
angioplasties <- angioplasties %>% add_trace(x = ~x, y = ~y2, type = 'bar',
                         name = 'Different Procedure',
                         text = y2, textposition = 'auto',
                         marker = list(color = '#546FBF',
                                       line = list(color = '#546FBF', width = 1.5)))
angioplasties <- angioplasties %>% layout(title = "Angioplasty frequency depending on previous procedure",
                      barmode = 'group',
                      xaxis = list(title = ""),
                      yaxis = list(title = "Number of Patients"))

angioplasties
```

